
## 0 Preparation step
# Create a folder called assignment 2:
```{r}
if(!file.exists("./assignment")){dir.create("./assignment")}
```

# Download and unzip file:
```{r}
fileurl <- "https://d396qusza40orc.cloudfront.net/exdata%2Fdata%2FNEI_data.zip"
download.file(fileurl, destfile = "./assignment/assignment.zip")
unzip(zipfile = "./assignment/assignment.zip", exdir = "./assignment")
```

# Read the file into R and check and class of each variable:
```{r}
setwd("D:/Statistics/R/R data/assignment2/assignment")
NEI <- readRDS("summarySCC_PM25.rds")
SCC <- readRDS("Source_Classification_Code.rds")
lapply(NEI, class); lapply(SCC, class)
```

## PLot 6 Compare emissions from motor vehicle sources in Baltimore City with emissions from motor vehicle sources in Los Angeles County, California (\color{red}{\verb|fips == "06037"|}fips == "06037"). Which city has seen greater changes over time in motor vehicle emissions?

# Set the condition for motor vehicals
```{r}
condition <- grepl("vehicle", SCC[, 8], ignore.case=TRUE)
vehiclesSCC <- SCC[condition,]$SCC
vehiclesNEI <- NEI[NEI$SCC %in% vehiclesSCC,]
```

# Take out the motor vehicals of Baltimore
```{r}
vehiclesBaltimoreNEI <- vehiclesNEI[vehiclesNEI$fips=="24510",]
vehiclesBaltimoreNEI$city <- "Baltimore City"
```

# Take out the motor vehicals of LosAngeles
```{r}
vehiclesLANEI <- vehiclesNEI[vehiclesNEI$fips=="06037",]
vehiclesLANEI$city <- "Los Angeles County"
```

# Combine the 2 dataframe according to row
```{r}
Combine <- rbind(vehiclesBaltimoreNEI,vehiclesLANEI)
```

# Drawing the final plot
```{r}
library(ggplot2)
Combine$year <- as.factor(Combine$year)
bar <- ggplot(Combine, aes(city, Emissions, fill=year)) 
bar + stat_summary(fun.y = sum, geom = "bar", position="dodge") + labs(x = "City", y = "Emissions", fill = "Year", title = "Baltimore City/Los Angeles County: Emissions of motor vehicle")
dev.copy(device = png, width = 480, height = 480, file = "Plot6.png")
dev.off()
```

