
## 0 Preparation step
# Create a folder called assignment 2:
```{r}
if(!file.exists("./assignment")){dir.create("./assignment")}
```

# Download and unzip file:
```{r}
fileurl <- "https://d396qusza40orc.cloudfront.net/exdata%2Fdata%2FNEI_data.zip"
download.file(fileurl, destfile = "./assignment/assignment.zip")
unzip(zipfile = "./assignment/assignment.zip", exdir = "./assignment")
```

# Read the file into R and check and class of each variable:
```{r}
setwd("D:/Statistics/R/R data/assignment2/assignment")
NEI <- readRDS("summarySCC_PM25.rds")
SCC <- readRDS("Source_Classification_Code.rds")
lapply(NEI, class); lapply(SCC, class)
```

## PLOT 4:Across the United States, how have emissions from coal combustion-related sources changed from 1999–2008?

# Merge the tables
```{r}
NEISCC <- merge(NEI, SCC, by="SCC")
library(dplyr)
NEISCCdp <- tbl_df(NEISCC)
```
# Search for coal and rename column 
```{r}
NEISCCdp <- mutate(NEISCCdp, coal = grepl("coal", NEISCCdp$Short.Name, ignore.case=TRUE))
EmissionsCoalYear <- summarize(group_by(filter(NEISCCdp, coal==TRUE),year),sum(Emissions))
colnames(EmissionsCoalYear) <- c("Year", "Emissions") 
```

# Convert to factor
```{r}
EmissionsCoalYear$Year <- as.factor(EmissionsCoalYear$Year)
lapply(EmissionsCoalYear, class)
```

# PLot4: Across the United States, how have emissions from coal combustion-related sources changed from 1999–2008?

```{r}
library(ggplot2)
g <- ggplot(EmissionsCoalYear, aes(Year, Emissions))
g+geom_bar(stat='identity')+labs(title="Emissions from coal combustion-related sources", x="Years",y="Emissions (PM 2.5)")
dev.copy(device = png, width = 480, height = 480, file = "Plot4.png")
dev.off()
```

