
## 0 Preparation step
# Create a folder called assignment 2:
```{r}
if(!file.exists("./assignment")){dir.create("./assignment")}
```

# Download and unzip file:
```{r}
fileurl <- "https://d396qusza40orc.cloudfront.net/exdata%2Fdata%2FNEI_data.zip"
download.file(fileurl, destfile = "./assignment/assignment.zip")
unzip(zipfile = "./assignment/assignment.zip", exdir = "./assignment")
```

# Read the file into R and check and class of each variable:
```{r}
setwd("D:/Statistics/R/R data/assignment2/assignment")
NEI <- readRDS("summarySCC_PM25.rds")
SCC <- readRDS("Source_Classification_Code.rds")
lapply(NEI, class); lapply(SCC, class)
```

## PLOT 2: Have total emissions from PM2.5 decreased in the Baltimore City, Maryland (\color{red}{\verb|fips == "24510"|}fips == "24510") from 1999 to 2008?

# Extract data BaltimoreNEI from NEI
```{r}
baltimoreNEI <- NEI[NEI$fips=="24510",]
```

# Calculate the Emission Year of Baltimore

```{r}
baltimoreEmission <- aggregate(Emissions ~ year,baltimoreNEI, sum)
```

# Drawing barplot
```{r}
barplot(baltimoreEmission$Emissions, names.arg=baltimoreEmission$year, col="blue", xlab='Years', ylab='Emissions (PM 2.5)', main =  'Emissions (PM 2.5) per year')
dev.copy(device = png, width = 480, height = 480, file = "Plot2.png")
dev.off()
```

# Another solution using ggplot2 system (for double check)
```{r}
baltimoreNEI <- NEI[NEI$fips=="24510",]
baltimoreNEI[,6] = as.factor(baltimoreNEI[,6])
baltimoreNEI[,4] = as.numeric(baltimoreNEI[,4])
lapply(baltimoreNEI, class)
library(ggplot2)
bar <- ggplot(baltimoreNEI, aes(year, Emissions))
bar + stat_summary(fun.y = sum, geom = "bar")
dev.copy(device = png, width = 480, height = 480, file = "Plot2ggplot.png")
dev.off()
```




