
## 0 Preparation step
# Create a folder called assignment 2:
```{r}
if(!file.exists("./assignment")){dir.create("./assignment")}
```

# Download and unzip file:
```{r}
fileurl <- "https://d396qusza40orc.cloudfront.net/exdata%2Fdata%2FNEI_data.zip"
download.file(fileurl, destfile = "./assignment/assignment.zip")
unzip(zipfile = "./assignment/assignment.zip", exdir = "./assignment")
```

# Read the file into R and check and class of each variable:
```{r}
setwd("D:/Statistics/R/R data/assignment2/assignment")
NEI <- readRDS("summarySCC_PM25.rds")
SCC <- readRDS("Source_Classification_Code.rds")
lapply(NEI, class); lapply(SCC, class)
```

## PLOT 3: Of the four types of sources indicated by the \color{red}{\verb|type|}type (point, nonpoint, onroad, nonroad) variable, which of these four sources have seen decreases in emissions from 1999–2008 for Baltimore City? Which have seen increases in emissions from 1999–2008? Use the ggplot2 plotting system to make a plot answer this question.

# Extract data BaltimoreNEI from NEI
```{r}
baltimoreNEI <- NEI[NEI$fips=="24510",]
```

# Drawing bar plot for 4 years
```{r}
bar <- ggplot(baltimoreNEI, aes(type, Emissions, fill = year))
bar + stat_summary(fun.y = sum, geom = "bar", position="dodge") + labs(x = "Type", y = "Emisions", fill = "Year")
dev.copy(device = png, width = 480, height = 480, file = "Plot3.png")
dev.off()
```



